Standartox: A tool to derive exposure endpoints from chemical test results

### 2019-10-15 article/supplement/r-package-list.tex
article

R Core Team (2019).

@@

Wickham H, Hester J, Chang W (2019).

@@

Lang DT, team tC (2019).

@@

Wickham H (2019).

@@

Bengtsson H (2019).

@@

Hiebert J (2016).

@@

Ooms J (2014).

@@

Wickham H, Bryan J (2019).

@@

Walker A (2019).

@@

Henry L, Wickham H (2019).

@@

Dowle M, Srinivasan A (2019).

@@

Conway J, Eddelbuettel D, Nishiyama T, Prayaga SK, Tiffin N (2017).

@@

R Special Interest Group on Databases (R-SIG-DB), Wickham H, Müller K (2018).

@@

Oksanen J, Blanchet FG, Friendly M, Kindt R, Legendre P, McGlinn D, Minchin PR, O'Hara RB, Simpson GL, Solymos P, Stevens MHH, Szoecs E, Wagner H (2019).

@@

Wickham H (2011).

@@

Komsta L (2011).

@@

Wickham H (2016).

@@

Slowikowski K (2019).

@@

Wilke C (2019).

@@

Neuwirth E (2014).

@@

Tennekes M (2017).

@@

Chamberlain S, Barve V, Mcglinn D, Oldoni D, Desmet P, Geffert L, Ram K (2019).

@@

Chamberlain S, Boettiger C (2017).
``R Python, and Ruby clients for GBIF species occurrence data.''
\emph{PeerJ PrePrints}.
\url{https://doi.org/10.7287/peerj.preprints.3304v1}.
Scott Chamberlain, Eduard Szocs (2013).
``taxize - taxonomic search and retrieval in R.''
\emph{F1000Research}.
\url{http://f1000research.com/articles/2-191/v2}.

Chamberlain S, Szoecs E, Foster Z, Arendsee Z, Boettiger C, Ram K, Bartomeus I, Baumgartner J, O'Donnell J, Oksanen J, Tzovaras BG, Marchand P, Tran V, Salmon M, Li G, Grenié M (2019).
\emph{taxize: Taxonomic information from around the web}.
R package version 0.9.7, \url{https://github.com/ropensci/taxize}.
Arel-Bundock V, Enevoldsen N, Yetman C (2018).
``countrycode: An R package to convert country names and country codes.''
\emph{Journal of Open Source Software}, \bold{3}(28), 848.
\url{https://doi.org/10.21105/joss.00848}.
Microsoft, Weston S (2017).
\emph{foreach: Provides Foreach Looping Construct for R}.
R package version 1.4.4, \url{https://CRAN.R-project.org/package=foreach}.
Corporation M, Weston S (2018).
\emph{doParallel: Foreach Parallel Adaptor for the 'parallel' Package}.
R package version 1.0.14, \url{https://CRAN.R-project.org/package=doParallel}.
Klik M (2019).
\emph{fst: Lightning Fast Serialization of Data Frames for R}.
R package version 0.9.0, \url{https://CRAN.R-project.org/package=fst}.
Xie Y, Cheng J, Tan X (2019).
\emph{DT: A Wrapper of the JavaScript Library 'DataTables'}.
R package version 0.7, \url{https://CRAN.R-project.org/package=DT}.
Tennekes M (2017).
\emph{treemap: Treemap Visualization}.
R package version 2.4-2, \url{https://CRAN.R-project.org/package=treemap}.

>>>>

\newline R Core Team (2019).

@@

\newline Wickham H, Hester J, Chang W (2019).

@@

\newline Lang DT, team tC (2019).

@@

\newline Wickham H (2019).

@@

\newline Bengtsson H (2019).

@@

\newline Hiebert J (2016).

@@

\newline Ooms J (2014).

@@

\newline Wickham H, Bryan J (2019).

@@

\newline Walker A (2019).

@@

\newline Henry L, Wickham H (2019).

@@

\newline Dowle M, Srinivasan A (2019).

@@

\newline Conway J, Eddelbuettel D, Nishiyama T, Prayaga SK, Tiffin N (2017).

@@

\newline R Special Interest Group on Databases (R-SIG-DB), Wickham H, Müller K (2018).

@@

\newline Oksanen J, Blanchet FG, Friendly M, Kindt R, Legendre P, McGlinn D, Minchin PR, O'Hara RB, Simpson GL, Solymos P, Stevens MHH, Szoecs E, Wagner H (2019).

@@

\newline Wickham H (2011).

@@

\newline Komsta L (2011).

@@

\newline Wickham H (2016).

@@

\newline Slowikowski K (2019).

@@

\newline Wilke C (2019).

@@

\newline Neuwirth E (2014).

@@

\newline Tennekes M (2017).

@@

\newline Chamberlain S, Barve V, Mcglinn D, Oldoni D, Desmet P, Geffert L, Ram K (2019).

@@

Chamberlain S, Boettiger C (2017).
``R Python, and Ruby clients for GBIF species occurrence data.''
\emph{PeerJ PrePrints}.
\url{https://doi.org/10.7287/peerj.preprints.3304v1}.
\newline Scott Chamberlain, Eduard Szocs (2013).
``taxize - taxonomic search and retrieval in R.''
\emph{F1000Research}.
\url{http://f1000research.com/articles/2-191/v2}.

Chamberlain S, Szoecs E, Foster Z, Arendsee Z, Boettiger C, Ram K, Bartomeus I, Baumgartner J, O'Donnell J, Oksanen J, Tzovaras BG, Marchand P, Tran V, Salmon M, Li G, Grenié M (2019).
\emph{taxize: Taxonomic information from around the web}.
R package version 0.9.7, \url{https://github.com/ropensci/taxize}.
\newline Arel-Bundock V, Enevoldsen N, Yetman C (2018).
``countrycode: An R package to convert country names and country codes.''
\emph{Journal of Open Source Software}, \bold{3}(28), 848.
\url{https://doi.org/10.21105/joss.00848}.
\newline Microsoft, Weston S (2017).
\emph{foreach: Provides Foreach Looping Construct for R}.
R package version 1.4.4, \url{https://CRAN.R-project.org/package=foreach}.
\newline Corporation M, Weston S (2018).
\emph{doParallel: Foreach Parallel Adaptor for the 'parallel' Package}.
R package version 1.0.14, \url{https://CRAN.R-project.org/package=doParallel}.
\newline Klik M (2019).
\emph{fst: Lightning Fast Serialization of Data Frames for R}.
R package version 0.9.0, \url{https://CRAN.R-project.org/package=fst}.
\newline Xie Y, Cheng J, Tan X (2019).
\emph{DT: A Wrapper of the JavaScript Library 'DataTables'}.
R package version 0.7, \url{https://CRAN.R-project.org/package=DT}.
\newline Tennekes M (2017).
\emph{treemap: Treemap Visualization}.
R package version 2.4-2, \url{https://CRAN.R-project.org/package=treemap}.
\newline
